Efficiently Handling Guards in the Low Level Design of RPython's tracing JIT

### 2012-08-02 talk/vmil2012/paper.tex
add emails

\authorinfo{David Schneider$^{a}$ \and Carl Friedrich Bolz$^a$}
           {$^a$Heinrich-Heine-Universität Düsseldorf, STUPS Group, Germany
           }
           {XXX emails}

>>>>

\authorinfo{David Schneider$^{a}$ \and Carl Friedrich Bolz$^a$}
           {$^a$Heinrich-Heine-Universität Düsseldorf, STUPS Group, Germany
           }
           {david.schneider@uni-duesseldorf.de \and cfbolz@gmx.de}
